---
title: "secseq igg"
output: html_document
---

```{r}
library(dplyr)
library(pheatmap)
library(dendextend)
library(tibble)
```

# read in data

data is normalized mean expression of secRecon genes annotated in the subsystems important in explaining heterogeneity of secreted IgG; 

mean expression has been calculated within random subsampled pseudobulk groups within each IgG cluster (Leiden clusters 0,1,2,4,10); refer to 2_Dominance-Analysis.ipynb

genes that are 0 across all groups have been removed
```{r}
# load in saved image
load("4_IgGpopulation_corr.RData")
```


```{r}
data = read.csv('../data/dominance_analysis/igg_cluster_pseudobulk_secrecon_mean.csv',row.names = 1)
dim(data)
data
```

# spearman corr for secRecon gene expression across all groups
```{r fig.height=3, fig.width=3}
corrplot::corrplot(cor.gene,
                   method='square',order='original',addrect = 3,tl.pos = 'n',addgrid.col=NA,addCoef.col = NULL,cl.cex=1.2)
```


Dendrogram creation from hierarchical clustering of gene expression and Baker's gamma index correlation of dendrograms

# create dendrograms per cluster
```{r}
# separate data per cluster
data.cluster <- list()
clusters <- sapply(colnames(data), function(x) {strsplit(x,'[_]')[[1]][1]})
# clusters

for (c in unique(clusters)){
  data.cluster[[c]] <- data[,names(clusters[clusters == c])]
}

lapply(data.cluster,dim)

```


```{r}
# calculate similarity distance between genes using cosine distance
dist.cluster <- lapply(data.cluster,function(x) {
  as.dist(1-cosine(t(data.frame(x))))}) 

# perform hierarchical clustering using average linkage
## convert to dendrogram
hc.cluster <- lapply(dist.cluster,function(x) {hclust(x, method='average') %>% as.dendrogram()})
```


```{r}
dend.cluster <- dendlist('X0'=hc.cluster$X0, 
                 'X1'=hc.cluster$X1, 
                 'X2'=hc.cluster$X2, 
                 'X4'=hc.cluster$X4, 
                 'X10'=hc.cluster$X10)
```

```{r}
# correlate with bakers gamma
dend.cluster.cor = cor.dendlist(dend.cluster, method = 'baker')
```

```{r}
# rename/reorder cluster names
c.order <- c(10,4,2,1,0)
dend.cluster.cor.rn <- dend.cluster.cor
colnames(dend.cluster.cor.rn) <- stringr::str_replace(colnames(dend.cluster.cor.rn),'X','cluster ')
rownames(dend.cluster.cor.rn) <- stringr::str_replace(rownames(dend.cluster.cor.rn),'X','cluster ')
dend.cluster.cor.rn <- dend.cluster.cor.rn[paste('cluster',c.order),paste('cluster',c.order)]
dend.cluster.cor.rn
```

summarize Bakers gamma dendrogram correlation using corrplot
 
```{r fig.height=3, fig.width=3}
corrplot::corrplot(dend.cluster.cor.rn,method='square',order='original',addCoef.col = 'white',type = 'lower',number.cex=1.5,tl.col='black',tl.srt = 45,tl.cex=1.5,cl.pos='n')
```


```{r}
corrplot::corrplot(dend.cluster.cor,
                   method='square',order='hclust',addrect = 2,hclust.method='average', addCoef.col = 'black')

```